---
title: "Figure Supp3"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE, warning = FALSE, comment = NA)

freshr::freshr()
library(dplyr)
library(car)
library(sjPlot)
library(gridExtra)
library(knitr)
library(tidyverse)
library(ggbeeswarm)
library(ggthemes)
library(emmeans)
library(parameters)
library(bayestestR)
library(ggplot2)
library(ggsci)
library(tinytex)
library(extrafont)
library(ggpubr)
#list the Fonts in windows
#windowsFonts()
#set-theme for figure
theme_set (theme_classic(base_size = 10, base_family = "sans"))

##libraries for color
library(ggsci)
library(wesanderson)
#names(wes_palettes)
library(colorBlindness)
library(viridis)
#dependent function
library(here)
source (here("src", "Develop_Function_posthoc_20230219.R"))
```

```{r,echo = FALSE}
#Figure plotting function
plot_raw = function(var, data = df_lite, title = var,
                    y_breaks = c(1:6 * 0.5), 
                    y_limits = c(0, 2), 
                    legend_position = c(0.4, 0.5)) {
df_lite %>%
   select(f.age, sex, f.layer, var) %>%
   tidyr::unite("group", sex:f.layer, sep = "-", remove = FALSE) %>%
   ggplot(aes(x = f.age, y = get(var), color = group, group = group)) + 
   #ggbeeswarm::geom_beeswarm(dodge.width = 0.4, alpha = 0.3) +
   stat_summary(fun = "mean", geom = "line", linewidth = 0.4,
                position = position_dodge(width = 0.4)) +
   stat_summary(fun.data = "mean_cl_boot", size = 0.02, linewidth = 0.4, 
                 position = position_dodge(width = 0.4)) +
   ggtitle(title) +
   scale_y_continuous(breaks = y_breaks, limits = y_limits) +
   labs(x = "", y = "") + 
   theme( legend.text = element_text(color = "black", size  = "8"),
          legend.position = legend_position,
          legend.title = element_blank(),
          axis.text.x = element_text(color = "black", size = "8"),
          axis.line.x.bottom = element_line (linewidth = 1/4),
          axis.text.y = element_text(color = "black", size = "8"),
          axis.line.y = element_line(linewidth = 1/4), 
          axis.ticks.x = element_blank(),
          plot.background = element_blank(),
          plot.margin = unit(c(0,-0.15,0,0), 'cm')) + 
    ggsci::scale_color_locuszoom() -> p
return(p)
  
}
```

### Figure Supp 3 - Kmean_CovM
```{r}
load (here("output","2023-02-19_SummaryDevAll_Kmean_CovM_withCorr_Dist_20230113.RData"))

a <-plot_raw("s_assemblies",
         y_breaks = c(1:6 * 10), y_limits = c(0, 50),
        legend_position = "none", title = "Event-single cluster")

b <-plot_raw("m_assemblies",
         y_breaks = c(1:6 * 2), y_limits = c(0, 10),
        legend_position = "none",title = "Event-multiple cluster")


c <-plot_raw("silhs_mean_before_stat",
         y_breaks = c(1:6 * 0.1), y_limits = c(0, 0.5),
        legend_position = "none", title = "Silhoutte")

d <-plot_raw("n_cls",
         y_breaks = c(1:6 * 2), y_limits = c(0, 10),
                legend_position = "none",title = "Subnetwork #")

```

```{r,fig.width = 8, fig.asp = 0.3, echo=FALSE}
ggarrange(a,b,c,d,
          ncol = 4, nrow = 1)
```

##### Figure Supp 3 - Kmean_CovM -Silhouette
```{r}
report_main_effect("silhs_mean_before_stat")
report_inter_age_sex_layer("silhs_mean_before_stat")
```

##### Figure Supp 3 - Kmean_CovM - subntwork #
```{r}
report_main_effect("n_cls")
report_inter_age_sex_layer("n_cls")
```


### Figure Supp 3 - Kmean_Cosine
```{r}
load (here("output","2023-02-19_SummaryDevAll_Kmean_Cosine_withCorr_20230113.RData"))

e <-plot_raw("s_assemblies",
         y_breaks = c(1:6 * 10), y_limits = c(0, 50),
        legend_position = "none", title = "Event-single cluster")

f <-plot_raw("m_assemblies",
         y_breaks = c(1:6 * 2), y_limits = c(0, 10),
        legend_position = "none",title = "Event-multiple cluster")


g <-plot_raw("silhs_mean_before_stat",
         y_breaks = c(1:6 * 0.1), y_limits = c(0, 0.5),
        legend_position = "none", title = "Silhoutte")

h <-plot_raw("n_cls",
         y_breaks = c(1:6 * 2), y_limits = c(0, 10),
                legend_position = "none",title = "Subnetwork #")

```

```{r,fig.width = 8, fig.asp = 0.3, echo=FALSE}
ggarrange(e,f,g,h,
          ncol = 4, nrow = 1)
```


##### Figure Supp 3 - Kmean_Cosine - Silhouette
```{r}
report_main_effect("silhs_mean_before_stat")
report_inter_age_sex_layer("silhs_mean_before_stat")
```

##### Figure Supp 3 - Kmean_Cosine - subntwork
```{r}
report_main_effect("n_cls")
report_inter_age_sex_layer("n_cls")
```


### Figure Supp 3 - Kmean_Jaccard
```{r}
load (here("output","2023-02-19_SummaryDevAll_Kmean_Jaccard_withCorr_20230113.RData"))

i <-plot_raw("s_assemblies",
         y_breaks = c(1:6 * 10), y_limits = c(0, 50),
        legend_position = "none")

j <-plot_raw("m_assemblies",
         y_breaks = c(1:6 * 2), y_limits = c(0, 10),
        legend_position = "none")


k <-plot_raw("silhs_mean_before_stat",
         y_breaks = c(1:6 * 0.1), y_limits = c(0, 0.5),
        legend_position = "none")

l <-plot_raw("n_cls",
         y_breaks = c(1:6 * 2), y_limits = c(0, 10),
        legend_position = "none")
```

```{r,fig.width = 8, fig.asp = 0.3, echo=FALSE}
ggarrange(i,j,k,l,
          ncol = 4, nrow = 1)
```

##### Figure Supp 3 - Kmean_Jaccard - Silhouette
```{r}
report_main_effect("silhs_mean_before_stat")
report_inter_age_sex_layer("silhs_mean_before_stat")
```

##### Figure Supp 3 - Kmean_Jaccard - subntwork #
```{r}
report_main_effect("n_cls")
report_inter_age_sex_layer("n_cls")
```


### Figure Supp 3 - Community detection-uniform_CovM
```{r}
load (here("output","2023-02-19_SummaryDevAll_CommDetecUni_CovM_withCorrl_20230113.RData"))
m <-plot_raw("s_assemblies",
         y_breaks = c(1:6 * 10), y_limits = c(0, 50),
        legend_position = "none", title = "Event-single cluster")

n <-plot_raw("m_assemblies",
         y_breaks = c(1:6 * 2), y_limits = c(0, 10),
        legend_position = "none",title = "Event-multiple cluster")


o <-plot_raw("silhs_mean_before_stat",
         y_breaks = c(1:6 * 0.1), y_limits = c(0, 0.5),
        legend_position = "none", title = "Silhoutte")

p <-plot_raw("n_cls",
         y_breaks = c(1:6 * 2), y_limits = c(0, 10),
                legend_position = "none",title = "Subnetwork #")

```

```{r,fig.width = 8, fig.asp = 0.3, echo=FALSE}
ggarrange(m,n,o,p,
          ncol = 4, nrow = 1)
```

##### Figure Supp 3 - Community detection-uniform_CovM - Silhouette
```{r}
report_main_effect("silhs_mean_before_stat")
report_inter_age_sex_layer("silhs_mean_before_stat")
```

##### Figure Supp 3 - Community detection-uniform_CovM - subnetwork #
```{r}
report_main_effect("n_cls")
report_inter_age_sex_layer("n_cls")
```


### Figure Supp 3 - Community detection-Asymmetric_CovM
```{r}
load (here("output","2023-02-19_SummaryDevAll_CommDetecAsy_CovM_withCorr_20230113.RData"))

q <-plot_raw("s_assemblies",
         y_breaks = c(1:6 * 10), y_limits = c(0, 50),
        legend_position = "none", title = "Event-single cluster")

r <-plot_raw("m_assemblies",
         y_breaks = c(1:6 * 2), y_limits = c(0, 10),
        legend_position = "none",title = "Event-multiple cluster")


s <-plot_raw("silhs_mean_before_stat",
         y_breaks = c(1:6 * 0.1), y_limits = c(0, 0.5),
        legend_position = "none", title = "Silhoutte")

t <-plot_raw("n_cls",
         y_breaks = c(1:6 * 2), y_limits = c(0, 10),
                legend_position = "none",title = "Subnetwork #")

```

```{r,fig.width = 8, fig.asp = 0.3, echo=FALSE}
ggarrange(q,r,s,t,
          ncol = 4, nrow = 1)
```

##### Figure Supp 3 - Community detection-Asymmetric_CovM -Silhouette
```{r}
report_main_effect("silhs_mean_before_stat")
report_inter_age_sex_layer("silhs_mean_before_stat")
```

##### Figure Supp 3 - Community detection-Asymmetric_CovM- subnetwork #
```{r}
report_main_effect("n_cls")
report_inter_age_sex_layer("n_cls")
```



