---
title: "Figure Supp8-additional clustering algorithm: subnetwork configuration and tCC in subnetwork"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE, warning = FALSE, comment = NA)

freshr::freshr()
library(readxl)
library(janitor)
library(dplyr)
library(car)
library(sjPlot)
library(gridExtra)
library(knitr)
library(tidyverse)
library(ggbeeswarm)
library(ggthemes)
library(emmeans)
library(parameters)
library(bayestestR)
library(ggplot2)
library(ggsci)
library(tinytex)
library(extrafont)
library(ggpubr)
#list the Fonts in windows
#windowsFonts()
#set-theme for figure
theme_set (theme_classic(base_size = 10, base_family = "sans"))

##libraries for color
library(ggsci)
library(wesanderson)
#names(wes_palettes)
library(colorBlindness)
library(viridis)
#dependent function
library(here)
source (here("src", "Develop_Function_posthoc_20240411.R"))
```

```{r,echo = FALSE}
#Figure plotting function
plot_raw = function(var, data = df_lite, title = var,
                    y_breaks = c(1:6 * 0.5), 
                    y_limits = c(0, 2), 
                    legend_position = c(0.4, 0.5)) {
df_lite %>%
   select(f.age, sex, f.layer, var) %>%
   tidyr::unite("group", sex:f.layer, sep = "-", remove = FALSE) %>%
   ggplot(aes(x = f.age, y = get(var), color = group, group = group)) + 
   #ggbeeswarm::geom_beeswarm(dodge.width = 0.4, alpha = 0.3) +
   stat_summary(fun = "mean", geom = "line", linewidth = 0.4,
                position = position_dodge(width = 0.4)) +
   stat_summary(fun.data = "mean_cl_boot", size = 0.02, linewidth = 0.4, 
                 position = position_dodge(width = 0.4)) +
   ggtitle(title) +
   scale_y_continuous(breaks = y_breaks, limits = y_limits) +
   labs(x = "", y = "") + 
   theme( legend.text = element_text(color = "black", size  = "8"),
          legend.position = legend_position,
          legend.title = element_blank(),
          axis.text.x = element_text(color = "black", size = "8"),
          axis.line.x.bottom = element_line (linewidth = 1/4),
          axis.text.y = element_text(color = "black", size = "8"),
          axis.line.y = element_line(linewidth = 1/4), 
          axis.ticks.x = element_blank(),
          plot.background = element_blank(),
          plot.margin = unit(c(0,-0.15,0,0), 'cm')) + 
    ggsci::scale_color_locuszoom() -> p
return(p)
  
}
```


### Figure Supp 8A - Kmean_CovM
```{r}
load (here("output","SummaryDevAll_Kmean_CovM_withCorrDistArea.RData"))
```

```{r}
a <-plot_raw("cells_in_one_assembly",
         y_breaks = c(1:10 * 20), y_limits = c(0, 80),
        legend_position = "none", title = "Single-cluster (%)")

b <-plot_raw("cells_not_in_assembly",
         y_breaks = c(1:10 * 20), y_limits = c(0, 80),
        legend_position = "none",title = "Non-cluster (%)")

c <-plot_raw("cells_in_many_assembly",
         y_breaks = c(1:10 * 20), y_limits = c(0, 80),
        legend_position = "none", title = "Multiple-cluster (%)")

d <-plot_raw("in_r_mean",
         y_breaks = c(1:6 * 0.2), y_limits = c(0, 1),
                legend_position = "",title = "tCC in subnetwork")

```

```{r,fig.width = 8, fig.asp = 0.3, echo=FALSE}
ggarrange(a,b,c,d,
          ncol = 4, nrow = 1)
```

##### Figure Supp 8A - Kmean_CovM - Single-cluster
```{r}
report_main_effect("cells_in_one_assembly")
report_inter_age_sex_layer("cells_in_one_assembly")
```

##### Figure Supp 8A - Kmean_CovM - Non-cluster
```{r}
report_main_effect("cells_not_in_assembly")
report_inter_age_sex_layer("cells_not_in_assembly")
```

##### Figure Supp 8A - Kmean_CovM - Multiple-cluster
```{r}
report_main_effect("cells_in_many_assembly")
report_inter_age_sex_layer("cells_in_many_assembly")
```

##### Figure Supp 8A - Kmean_CovM - tCC in subnetwork
```{r}
report_main_effect("in_r_mean")
report_inter_age_sex_layer("in_r_mean")
```


### Figure Supp 8B - Community detection-uniform_CovM
```{r}
load (here("output","SummaryDevAll_CommUni_CovM_withCorrDistArea.RData"))
```

```{r}
e <-plot_raw("cells_in_one_assembly",
         y_breaks = c(1:10 * 20), y_limits = c(0, 80),
        legend_position = "none", title = "Single-cluster (%)")

f <-plot_raw("cells_not_in_assembly",
         y_breaks = c(1:10 * 20), y_limits = c(0, 80),
        legend_position = "none",title = "Non-cluster (%)")

g <-plot_raw("cells_in_many_assembly",
         y_breaks = c(1:10 * 20), y_limits = c(0, 80),
        legend_position = "none", title = "Multiple-cluster (%)")

h <-plot_raw("in_r_mean",
         y_breaks = c(1:6 * 0.2), y_limits = c(0, 1),
                legend_position = "none",title = "tCC in subnetwork")

```

```{r,fig.width = 8, fig.asp = 0.3, echo=FALSE}
ggarrange(e,f,g,h,
          ncol = 4, nrow = 1)
```


##### Figure Supp 8B - Community detection-uniform - Single-cluster
```{r}
report_main_effect("cells_in_one_assembly")
report_inter_age_sex_layer("cells_in_one_assembly")
```

##### Figure Supp 8B - Community detection-uniform- Non-cluster
```{r}
report_main_effect("cells_not_in_assembly")
report_inter_age_sex_layer("cells_not_in_assembly")
```

##### Figure Supp 8B - Community detection-uniform- Multiple-cluster
```{r}
report_main_effect("cells_in_many_assembly")
report_inter_age_sex_layer("cells_in_many_assembly")
```

##### Figure Supp 8B - Community detection-uniform- tCC in subnetwork
```{r}
report_main_effect("in_r_mean")
report_inter_age_sex_layer("in_r_mean")
```



### Figure Supp 8C - Community detection-Asymmetric_CovM
```{r}
load (here("output","SummaryDevAll_CommDetectAsy_CovM_withCorrDistArea.RData"))
```

```{r}
i <-plot_raw("cells_in_one_assembly",
         y_breaks = c(1:10 * 20), y_limits = c(0, 80),
        legend_position = "none", title = "Single-cluster (%)")

j <-plot_raw("cells_not_in_assembly",
         y_breaks = c(1:10 * 20), y_limits = c(0, 80),
        legend_position = "none",title = "Non-cluster (%)")

k <-plot_raw("cells_in_many_assembly",
         y_breaks = c(1:10 * 20), y_limits = c(0, 80),
        legend_position = "none", title = "Multiple-cluster (%)")

l <-plot_raw("in_r_mean",
         y_breaks = c(1:6 * 0.2), y_limits = c(0, 1),
                legend_position = "none",title = "tCC in subnetwork")

```

```{r,fig.width = 8, fig.asp = 0.3, echo=FALSE}
ggarrange(i,j,k,l,
          ncol = 4, nrow = 1)
```


##### Figure Supp 8C - Community detection-Asymmetric_CovM - Single-cluster
```{r}
report_main_effect("cells_in_one_assembly")
report_inter_age_sex_layer("cells_in_one_assembly")
```

##### Figure Supp 8C - Community detection-Asymmetric_CovM - Non-cluster
```{r}
report_main_effect("cells_not_in_assembly")
report_inter_age_sex_layer("cells_not_in_assembly")
```

##### Figure Supp 8C - Community detection-Asymmetric_CovM - Multiple-cluster
```{r}
report_main_effect("cells_in_many_assembly")
report_inter_age_sex_layer("cells_in_many_assembly")
```

##### Figure Supp 8C - Community detection-Asymmetric_CovM - tCC in subnetwork
```{r}
report_main_effect("in_r_mean")
report_inter_age_sex_layer("in_r_mean")
```



### Figure Supp 8D - DBSCAN_CovM
```{r}
load (here("output","SummaryDevAll_DBSCAN_CovM_withCorrDistArea.RData"))
```

```{r}
m <-plot_raw("cells_in_one_assembly",
         y_breaks = c(1:10 * 20), y_limits = c(0, 80),
        legend_position = "none", title = "Single-cluster (%)")

n <-plot_raw("cells_not_in_assembly",
         y_breaks = c(1:10 * 20), y_limits = c(0, 80),
        legend_position = "none",title = "Non-cluster (%)")

o <-plot_raw("cells_in_many_assembly",
         y_breaks = c(1:10 * 20), y_limits = c(0, 80),
        legend_position = "none", title = "Multiple-cluster (%)")

p <-plot_raw("in_r_mean",
         y_breaks = c(1:6 * 0.2), y_limits = c(0, 1),
         legend_position = "none",title = "tCC in subnetwork")

```

```{r,fig.width = 8, fig.asp = 0.3, echo=FALSE}
ggarrange(m,n,o,p,
          ncol = 4, nrow = 1)
```


##### Figure Supp 8D - DBSCAN_CovM - Single-cluster
```{r}
report_main_effect("cells_in_one_assembly")
report_inter_age_sex_layer("cells_in_one_assembly")
```

##### Figure Supp 8D - DBSCAN_CovM - Non-cluster
```{r}
report_main_effect("cells_not_in_assembly")
report_inter_age_sex_layer("cells_not_in_assembly")
```

##### Figure Supp 8D - DBSCAN_CovM - Multiple-cluster
```{r}
report_main_effect("cells_in_many_assembly")
report_inter_age_sex_layer("cells_in_many_assembly")
```

##### Figure Supp 8D - DBSCAN_CovM - tCC in subnetwork
```{r}
report_main_effect("in_r_mean")
report_inter_age_sex_layer("in_r_mean")
```


```{r,fig.width = 8, fig.asp = 1, echo=FALSE}
ggarrange(a,b,c,d,
          e,f,g,h,
          i,j,k,l,
          m,n,o,p,
          ncol = 4, nrow = 4)

ggsave("SupFig8.svg", plot = last_plot(), path =here("output_plot"),
       width = 7, height = 6, units = "in")

```

##### Figure Supp 8E - compare methods-- Event cluster # vs subnetwork #
```{r}
# import data
df_plot_pre = read_xlsx(
  here("data", "CompareAllMethod.xlsx"),
  sheet = "Sheet1")

# check column names
df_plot_pre = clean_names(df_plot_pre)


df_plot_pre <- df_plot_pre %>%
  rename(MethodName = method)
#variablenames = names(df_plot_pre)

# overview of the variables
#skimr::skim(df_plot_pre, c(all_of(variablenames)))

df_plot <- df_plot_pre %>%
  mutate(MethodName = gsub("CommDetectUni", "Uni", MethodName))%>%
  mutate(MethodName = gsub("CommDetectAsy", "Asy", MethodName))%>%
  mutate(f.MethodName = factor(MethodName, levels = c("Kmean", "Uni", "Asy","DBSCAN")))%>%
  mutate(f.age = factor(age))

# density estimates of response variables
#lapply(rv_list, function(x) with(df_lite, densityPlot(get(x), xlab = x)))

```

```{r,fig.width = 7, fig.asp = 0.3, echo=FALSE}

# define label
  age.label = c("P11", "P13", "P15", "P18", "P21")
  names(age.label) = c("11", "13", "15", "18", "21")

  # Creating the scatter plot with a trend line
ggplot(df_plot, aes(x = n_cls, y = n_cls_before_stat)) +
      geom_point(aes(color = f.MethodName),shape = 1) +  # Scatter plot
      ggsci::scale_color_locuszoom() +  # Outline color palette 
      #geom_smooth(method = "lm", se = FALSE, color = "blue") + # Trend line (linear model)
      #stat_cor(method = "spearman", label.x = 3, label.y = 70, size = 2) +  # Add correlation coefficient
      labs(x = "Subnetwork #", y = "Event cluster #") +
      facet_wrap(~ f.age, nrow = 1, ncol = 5,
                 strip.position = "top",labeller = labeller(f.age = age.label),
                 scales = "free_y") +
      scale_x_continuous(breaks = seq(0, 200, by =5), limits = c(0, 15)) +
      scale_y_continuous(breaks = seq(0, 200, by =30), limits = c(0, 90))+
      theme(
        legend.position = "",
        axis.line.x = element_line(linewidth = 1/4),
        axis.line.y = element_line(linewidth = 1/4),
        strip.background = element_rect(color = "black",linewidth = 0.5))
ggsave("ncl-cluster_corr_fig.svg", plot = last_plot(), path =here("output_plot"),
       
       width = 7.7, height = 2.5, units = "in")

```