---
title: "Figure 4 and Figure Supp4"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment = "")

freshr::freshr()
library(dplyr)
library(car)
library(sjPlot)
library(gridExtra)
library(knitr)
library(tidyverse)
library(ggbeeswarm)
library(ggthemes)
library(emmeans)
library(parameters)
library(bayestestR)
library(ggplot2)
library(ggsci)
library(tinytex)
library(extrafont)
#list the Fonts in windows
#windowsFonts()
#set-theme for figure
theme_set (theme_classic(base_size = 10, base_family = "sans"))

##libraries for color
library(ggsci)
library(wesanderson)
#names(wes_palettes)
library(colorBlindness)
library(viridis)
#dependent function
library(here)
source (here("src", "Develop_Function_posthoc_20240411.R"))
```


##### Figure 4A (Event frequency)
```{r}
#result source
load (here("output","SummaryDevAll_basicParameter.RData"))
```

```{r, fig.width = 3, fig.asp = 0.75, echo=FALSE}
plot_raw_boot_merge_sex ("event_freq",
                           y_breaks = seq(0, 6 , by=1),
                           y_limits = c(0, 3), 
                           legend_position = "right",
                           title = "")
ggsave("event_freq_allage.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3, units = "in")
```

```{r}
report_main_effect("event_freq")
report_inter_age_sex_layer("event_freq")
```


##### Figure 4B (Synchrony frequency)
```{r, fig.width = 3, fig.asp = 0.75, echo=FALSE}
plot_raw_boot_merge_sex ("synchrony_freq",
                           y_breaks = seq(0, 6 , by=1),
                           y_limits = c(0, 3), 
                           legend_position = "right",
                           title = "")
ggsave("synchrony_freq_allage.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3, units = "in")
```

```{r}
report_main_effect("synchrony_freq")
report_inter_age_sex_layer("synchrony_freq")
```


##### Figure Supp4A (Pearson correlation coefficient)
```{r}
#result source
load (here("output","SummaryDevAll_Kmean_CovM_withCorrDistArea.RData"))
```

```{r, fig.width = 3, fig.asp = 0.8, echo=FALSE}
plot_raw_boot_facet_sex ("zf_r_allpair_mean",
                           y_breaks = seq(0,1, by= 0.2), 
                           y_limits = c(0.2, 1), 
                           legend_position = "",
                           title = "") 

ggsave("zf_r_allpair_mean.svg", plot = last_plot(), path =here("output_plot"),
       width = 3.7, height = 3, units = "in")
```

```{r}
report_main_effect("zf_r_allpair_mean")
report_inter_age_sex_layer("zf_r_allpair_mean")
```


##### Figure Supp4B (Mutual information)
```{r}
#result source
load (here("output","SummaryDevAll_Kmean_CovM_MI_Corr.RData"))
```

```{r, fig.width = 3, fig.asp = 0.8, echo=FALSE}
plot_raw_boot_facet_sex ("zf_r_allpair_mean",
                           y_breaks = seq(0,2, by= 0.2), 
                           y_limits = c(0, 1.2), 
                           legend_position = "",
                           title = "") 

ggsave("MI_zf_r_allpair_mean.svg", plot = last_plot(), path =here("output_plot"),
       width = 3.7, height = 3, units = "in")
```

```{r}
report_main_effect("zf_r_allpair_mean")
report_inter_age_sex_layer("zf_r_allpair_mean")
```


##### Figure 4C (subnetwork #)
```{r}
#result source
load (here("output","SummaryDevAll_Kmean_CovM_withCorrDistArea.RData"))
```

```{r, fig.width = 3, fig.asp = 0.75, echo=FALSE}
plot_raw_boot_merge_sex ("n_cls",
                           y_breaks = seq(0,15, by= 3), 
                           y_limits = c(0, 15), 
                           legend_position = "right",
                           title = "") 

ggsave("n_cls_all_age.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3, units = "in")
```

```{r}
report_main_effect("n_cls")
report_inter_age_sex_layer("n_cls")
```


##### Figure 4D (Silhouette value)
```{r, fig.width = 3, fig.asp = 0.75, echo=FALSE}
plot_raw_boot_facet_sex ("silhs_mean_before_stat",
                           y_breaks = seq(0,6, by= 0.2), 
                           y_limits = c(0, 0.8), 
                           legend_position = "right",
                           title = "") 

ggsave("silh_allage.svg", plot = last_plot(), path =here("output_plot"),
       width = 4, height = 3, units = "in")
```

```{r}
report_main_effect("silhs_mean_before_stat")
report_inter_age_sex_layer("silhs_mean_before_stat")
```


##### Figure 4E (tetrachoric correlation-in the same subnetwork)

```{r, fig.width = 5, fig.asp = 0.5,echo=FALSE}
plot_raw_boot_facet_sex("in_r_mean",
                         y_breaks = seq(0.1,6, by=0.3), 
                         y_limits = c(0.1, 1),
                         legend_position = "right",
                         title = "")
ggsave("in_r_mean_allage.svg", plot = last_plot(), path =here("output_plot"),
       width = 4, height = 2.8, units = "in")
```

```{r}
report_main_effect("in_r_mean")
report_inter_age_sex_layer("in_r_mean")
```



##### Figure 4F (single-cluster(%))
```{r, fig.width = 3, fig.asp = 0.75, echo=FALSE}
plot_raw_boot_merge_sex ("cells_in_one_assembly",
                           y_breaks = seq(0, 100 , by=20),
                           y_limits = c(0, 100), 
                           legend_position = "right",
                           title = "")
ggsave("cells_in_one_assembly_allage.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3, units = "in")
```
```{r}
report_main_effect("cells_in_one_assembly")
report_inter_age_sex_layer("cells_in_one_assembly")
```


##### Figure 4G (Non-cluster(%))
```{r, fig.width = 3, fig.asp = 0.75, echo=FALSE}
plot_raw_boot_merge_sex ("cells_not_in_assembly",
                           y_breaks = seq(0, 100 , by=20),
                           y_limits = c(0, 100), 
                           legend_position = "right",
                           title = "")
ggsave("cells_not_in_assembly_allage.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3, units = "in")
```

```{r}
report_main_effect("cells_not_in_assembly")
report_inter_age_sex_layer("cells_not_in_assembly")
```



##### Figure 4H (Multiple-cluster(%))
```{r, fig.width = 3, fig.asp = 0.75, echo=FALSE}
plot_raw_boot_merge_sex ("cells_in_many_assembly",
                           y_breaks = seq(0, 100 , by=20),
                           y_limits = c(0, 100), 
                           legend_position = "right",
                           title = "")
ggsave("cells_in_many_assembly_allage.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3, units = "in")
```

```{r}
report_main_effect("cells_in_many_assembly")
report_inter_age_sex_layer("cells_in_many_assembly")
```


##### Figure Supp 4C (Pairwise distances between neurons)
````{r, fig.width = 5, fig.asp = 0.5,echo=FALSE}
plot_raw_boot_merge_sex("pw_neuron_neuron",
                         y_breaks = seq(0,400, by=100), 
                         y_limits = c(0, 300),
                         legend_position = "right",
                         title = "")
ggsave("pw_neuron_neuron_allage.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3, units = "in")
````

```{r}
report_main_effect("pw_neuron_neuron")
report_inter_age_sex_layer("pw_neuron_neuron")
```


##### Figure Supp 4D (Distance of neuron to subnetwork centroid)
````{r, fig.width = 5, fig.asp = 0.5,echo=FALSE}
plot_raw_boot_merge_sex("neuron_centroid",
                         y_breaks = seq(0,200, by=50), 
                         y_limits = c(0, 200),
                         legend_position = "right",
                         title = "")
ggsave("neuron_centroid_allage.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3, units = "in")
````

```{r}
report_main_effect("neuron_centroid")
report_inter_age_sex_layer("neuron_centroid")
```


##### Figure Supp 4E (Pairwise distances between centroids)
```{r, fig.width = 5, fig.asp = 0.5,echo=FALSE}
plot_raw_boot_merge_sex("centroid_centroid",
                         y_breaks = seq(0,400, by=100), 
                         y_limits = c(0, 400),
                         legend_position = "right",
                         title = "")
ggsave("centroid_centroid_allage.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3, units = "in")
```

```{r}
report_main_effect("centroid_centroid")
report_inter_age_sex_layer("centroid_centroid")
```


##### Figure Supp 4xxx (Subnetwrok area)
````{r, fig.width = 5, fig.asp = 0.5,echo=FALSE}
plot_raw_boot_merge_sex("subnetwork_area",
                         y_breaks = seq(0,500000, by=50000), 
                         y_limits = c(0, 150000),
                         legend_position = "",
                         title = "")
ggsave("subnetwork_area_allage.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3, units = "in")
````

```{r}
report_main_effect("subnetwork_area")
report_inter_age_sex_layer("subnetwork_area")
```


