---
title: "Figure 6 and Figure Supp6"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment = NA)

freshr::freshr()
library(dplyr)
library(car)
library(sjPlot)
library(gridExtra)
library(knitr)
library(tidyverse)
library(ggbeeswarm)
library(ggthemes)
library(emmeans)
library(parameters)
library(bayestestR)
library(ggplot2)
library(ggsci)
library(tinytex)
library(extrafont)
#list the Fonts in windows
#windowsFonts()
#set-theme for figure
theme_set (theme_classic(base_size = 10, base_family = "sans"))

##libraries for color
library(ggsci)
library(wesanderson)
#names(wes_palettes)
library(colorBlindness)
library(viridis)
#dependent function
library(here)
source (here("src", "WT_Dlx_GsDREADD_Function_posthoc_20230217.R"))
```

##### Figure 6C (Event frequency)
```{r}
#result source
load (here("output","2023-02-17_Caseboot_SummaryWT_Dlx_GsDREADD_basicPara_20230113.RData"))
```

```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_sex ("event_freq",
                           y_breaks = c(1:6 * 1), 
                           y_limits = c(0, 3), 
                           legend_position = "right",
                           title = "") 
```

```{r}
report_main("event_freq")
report_all_interaction_simple("event_freq", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```


##### Figure 6D (Synchrony frequency)
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_sex ("synchrony_freq",
                           y_breaks = c(1:6 * 1), 
                           y_limits = c(0, 4), 
                           legend_position = "right",
                           title = "") 
```

```{r}
report_main("synchrony_freq")
report_all_interaction_simple("synchrony_freq", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure 6E (Silhouette value)
```{r}
load (here("output","2023-02-17_Caseboot_SummaryWT_Dlx_GsDREADD_kmean_CovM_20230113.RData"))
```

```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_sex ("silhs_mean_before_stat",
                           y_breaks = c(1:6 * 0.2), 
                           y_limits = c(0, 0.6), 
                           legend_position = "right",
                           title = "") 
```

```{r}
report_main("silhs_mean_before_stat")
report_all_interaction_simple("silhs_mean_before_stat", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```




##### Figure 6F (Single-cluster (%))
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_sex ("cells_in_one_assembly",
                           y_breaks = c(1:6 * 20), 
                           y_limits = c(0, 100), 
                           legend_position = "right",
                           title = "") 
```

```{r}
report_main("cells_in_one_assembly")
report_all_interaction_simple("cells_in_one_assembly", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure 6G (Non-cluster (%))
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_sex ("cells_not_in_assembly",
                           y_breaks = c(1:6 * 20), 
                           y_limits = c(0, 100), 
                           legend_position = "right",
                           title = "") 
```

```{r}
report_main("cells_not_in_assembly")
report_all_interaction_simple("cells_not_in_assembly", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```


##### Figure 6H (Multiple-cluster (%))
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_sex ("cells_in_many_assembly",
                           y_breaks = c(1:6 * 20), 
                           y_limits = c(0, 100), 
                           legend_position = "right",
                           title = "") 
```

```{r}
report_main("cells_in_many_assembly")
report_all_interaction_simple("cells_in_many_assembly", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure supp6G Pearson Correlation- all pairs)
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_sex ("r_zf_allpair_mean",
                           y_breaks = c(1:6 * 0.2), 
                           y_limits = c(0, 1), 
                           legend_position = "right",
                           title = "") 
```

```{r}
report_main("r_zf_allpair_mean")
report_all_interaction_simple("r_zf_allpair_mean", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure supp6H (Subnetwork number)
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_sex ("n_cls",
                           y_breaks = c(1:6 * 5), 
                           y_limits = c(0, 15), 
                           legend_position = "right",
                           title = "") 
```

```{r}
report_main("n_cls")
report_all_interaction_simple("n_cls", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure supp6I (tCC - in the same subnetwork)
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_sex ("cluster_r_all_mean",
                           y_breaks = c(1:6 * 0.2), 
                           y_limits = c(0, 1), 
                           legend_position = "right",
                           title = "") 
```

```{r}
report_main("cluster_r_all_mean")
report_all_interaction_simple("cluster_r_all_mean", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure supp6J (Pairwise distances between neurons)
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_sex ("pw_neuron_neuron",
                           y_breaks = c(1:6 * 50), 
                           y_limits = c(0, 250), 
                           legend_position = "right",
                           title = "") 
```

```{r}
report_main("pw_neuron_neuron")
report_all_interaction_simple("pw_neuron_neuron", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure supp6K (Distance of neuron to subnetwork centroid)
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_sex ("neuron_centroid",
                           y_breaks = c(1:6 * 50), 
                           y_limits = c(0, 200), 
                           legend_position = "right",
                           title = "") 
```

```{r}
report_main("neuron_centroid")
report_all_interaction_simple("neuron_centroid", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure supp6L (Pairwise distances between subnetwork centroids)
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_sex ("centroid_centroid",
                           y_breaks = c(1:6 * 100), 
                           y_limits = c(0, 400), 
                           legend_position = "right",
                           title = "") 
```

```{r}
report_main("centroid_centroid")
report_all_interaction_simple("centroid_centroid", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```
