---
title: "Figure 5 and Figure Supp6"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment = "")

freshr::freshr()
library(dplyr)
library(car)
library(sjPlot)
library(gridExtra)
library(knitr)
library(tidyverse)
library(ggbeeswarm)
library(ggthemes)
library(emmeans)
library(parameters)
library(bayestestR)
library(ggplot2)
library(ggsci)
library(tinytex)
library(extrafont)
library(ggpubr)
#library(gridExtra)
library(cowplot)
#list the Fonts in windows
#windowsFonts()
#set-theme for figure
theme_set (theme_classic(base_size = 10, base_family = "sans"))

##libraries for color
library(ggsci)
library(wesanderson)
#names(wes_palettes)
library(colorBlindness)
library(viridis)
#dependent function
library(here)
source (here("src", "WT_Dlx_GsDREADD_Function_posthoc_20240503.R"))
```



##### Figure 5C (Event frequency)
```{r}
#result source
load (here("output","Kmean_CovM_SummaryWT_Dlx_GsDREADD_basicPara.RData"))
```

```{r, fig.width = 2, fig.asp = 1.5, echo=FALSE}
plot_raw_boot_facet_layer ("event_freq",
                           y_breaks = seq(0,6, by = 1), 
                           y_limits = c(0, 3), 
                           legend_position = "right",
                           title = "")

ggsave("CNO_event_freq.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3.5, units = "in")

```

```{r}
report_main("event_freq")
report_all_interaction_simple("event_freq", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure 5D (Synchrony frequency)
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_layer ("synchrony_freq",
                           y_breaks =seq(0,6, by= 1), 
                           y_limits = c(0, 4), 
                           legend_position = "right",
                           title = "")

ggsave("CNO_sync_freq.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3.5, units = "in")
```

```{r}
report_main("synchrony_freq")
report_all_interaction_simple("synchrony_freq", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure 5E (Silhouette value)
```{r}
load (here("output", "Kmean_CovM_SummaryWT_Dlx_GsDREADD.RData"))
```

```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_layer ("silhs_mean_before_stat",
                           y_breaks = seq(0,6, by = 0.2), 
                           y_limits = c(0, 0.6), 
                           legend_position = "right",
                           title = "")
ggsave("silh.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3.5, units = "in")

```

```{r}
report_main("silhs_mean_before_stat")
report_all_interaction_simple("silhs_mean_before_stat", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```


##### Figure 5F (Single-cluster (%))
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_layer ("cells_in_one_assembly",
                           y_breaks = seq(0,120, by= 20), 
                           y_limits = c(0, 100), 
                           legend_position = "right",
                           title = "") 

ggsave("cells_in_one_assembly.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3.5, units = "in")

```

```{r}
report_main("cells_in_one_assembly")
report_all_interaction_simple("cells_in_one_assembly", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure 5G (Non-cluster (%))
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_layer ("cells_not_in_assembly",
                           y_breaks = seq(0,120, by=20), 
                           y_limits = c(0, 100), 
                           legend_position = "right",
                           title = "")

ggsave("cells_not_in_assembly.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3.5, units = "in")

```

```{r}
report_main("cells_not_in_assembly")
report_all_interaction_simple("cells_not_in_assembly", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure 5H (Multiple-cluster (%))
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
plot_raw_boot_facet_layer ("cells_in_many_assembly",
                           y_breaks = seq(0, 120, by= 20), 
                           y_limits = c(0, 100), 
                           legend_position = "right",
                           title = "") 

ggsave("cells_in_many_assembly.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3.5, units = "in")

```

```{r}
report_main("cells_in_many_assembly")
report_all_interaction_simple("cells_in_many_assembly", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure supp6A (Pearson Correlation- all pairs)
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
 a <- plot_raw_boot_facet_layer ("zf_r_allpair_mean",
                           y_breaks = seq(0, 6, by= 0.2), 
                           y_limits = c(0.2, 1), 
                           legend_position = "",
                           title = "")
a

ggsave("pearson.svg", plot = last_plot(), path =here("output_plot"),
       width = 2, height = 3, units = "in")

```

```{r}
report_main("zf_r_allpair_mean")
report_all_interaction_simple("zf_r_allpair_mean", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure supp6B (MI Correlation- all pairs)
```{r}
#result source
load (file = here("output","SummaryWT_Dlx_GsDREADD_kmean_CovM_MI_Corr.RData"))
```

```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
b <- plot_raw_boot_facet_layer ("zf_r_allpair_mean",
                           y_breaks = seq(0,6, by= 0.2), 
                           y_limits = c(0, 1), 
                           legend_position = "none",
                           title = "")
b

ggsave("MI.svg", plot = last_plot(), path =here("output_plot"),
       width = 2, height = 3, units = "in")
```

```{r}
report_main("zf_r_allpair_mean")
report_all_interaction_simple("zf_r_allpair_mean", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure supp6C (Subnetwork number)
```{r}
load (here("output","Kmean_CovM_SummaryWT_Dlx_GsDREADD.RData"))
```

```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
c <-plot_raw_boot_facet_layer ("n_cls",
                           y_breaks = seq(0,100, by=3), 
                           y_limits = c(0, 12), 
                           legend_position = "",
                           title = "")
c

ggsave("ncls.svg", plot = last_plot(), path =here("output_plot"),
       width = 2, height = 3, units = "in")

```

```{r}
report_main("n_cls")
report_all_interaction_simple("n_cls", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure supp6D (tCC - in the same subnetwork)
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
d <-plot_raw_boot ("in_r_mean",
                y_breaks = seq(0, 6, by = 0.2), 
                y_limits = c(0.2, 1), 
                legend_position = "",
                  title = "")
d

ggsave("in_r_mean.svg", plot = last_plot(), path =here("output_plot"),
       width = 4, height = 3, units = "in")

```

```{r}
report_main("in_r_mean")
report_all_interaction_simple("in_r_mean", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure supp6D (Pairwise distances between neurons)

```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
e<-plot_raw_boot_facet_layer ("pw_neuron_neuron",
                           y_breaks = seq(0,500, by=50), 
                           y_limits = c(0, 250), 
                           legend_position = "",
                           title = "")
e

ggsave("pw_neuron_neuron.svg", plot = last_plot(), path =here("output_plot"),
       width = 2, height = 3, units = "in")

```

```{r}
report_main("pw_neuron_neuron")
report_all_interaction_simple("pw_neuron_neuron", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```


##### Figure supp6E (Distance of neuron to subnetwork centroid)
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
f <-plot_raw_boot_facet_layer ("neuron_centroid",
                           y_breaks = seq(0, 500, by=50), 
                           y_limits = c(0, 200), 
                           legend_position = "",
                           title = "")
f
ggsave("neuron_centroid.svg", plot = last_plot(), path =here("output_plot"),
       width = 2.5, height = 3.5, units = "in")

```

```{r}
report_main("neuron_centroid")
report_all_interaction_simple("neuron_centroid", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```



##### Figure supp6G (Pairwise distances between subnetwork centroids)
```{r, fig.width = 4, fig.asp = 1, echo=FALSE}
g<-plot_raw_boot_facet_layer ("centroid_centroid",
                           y_breaks = seq(0,500, by= 100), 
                           y_limits = c(0, 400), 
                           legend_position = "",
                           title = "")
g
ggsave("cetroid_centroid.svg", plot = last_plot(), path =here("output_plot"),
       width = 2, height = 3, units = "in")

```

```{r}
report_main("centroid_centroid")
report_all_interaction_simple("centroid_centroid", var_int1 = "p15_cno", var_int2 = "sex", var_int3 = "f.layer")
```


##### assemble figure
```{r, fig.width = 7, fig.asp = 0.8, echo=FALSE}
top_row <- plot_grid(a, b, d, nrow = 1, rel_widths = c(1, 1, 2))  # First row
bottom_row <- plot_grid(c, e, f, g, nrow = 1)  # Second row

final_plot <- plot_grid(top_row, bottom_row, ncol = 1, rel_heights = c(1, 1))  # Combine rows

# Display the final plot
final_plot

ggsave("Figure_S6.svg", plot = last_plot(), path =here("output_plot"),
       width = 7, height = 6, units = "in")

```
